### 2016-07-13 main text/draft.tex
Applying the minors corrections
after Dave's comments

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{mwe}    % loads »blindtext« and »graphicx«
\usepackage{subfig}

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $}
\newcommand \um    {$\mu$m}
%\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \GALEX {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~{\textsc II}]} 
\newcommand \oiii {[O~{\textsc III}]} 
\newcommand \hi {H~{\textsc I}\ }

@@

\begin{abstract} 
Galaxies are very complex systems; a complete understanding of them cannot be achieved only from studying linear or logarithmic correlations between their properties.
The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis. 
In the past few decades, a number of statistical methods have been developed and advanced to study and visualize complex datasets.
We used one of these methods to study the properties of nearby galaxies and create a clearer picture of them.
%Spatially resolved maps provide us with a unique view of the inside of galaxies. %and help better understand their properties.
In this project, we utilized the Kohonen Self Organizing Map (SOM) method to study observations of the nearby galaxies M31 and M101. %SOM is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data while preserving topological features of the original data. 
%We studied 10 regions in M31 and 8 regions in M101. 
%These regions were chosen based on the availability of mid-infrared spectroscopy data.
%For each region in M31, we had 46 data obtained through photometry, spectroscopy, and derived quantities (i.e., star formation rate, stellar mass, gas mass, etc.). 
%Using results from a correlation coefficient matrix, we reduced the dimension of this dataset and then trained the SOM using the new subset of data. 
We created SOMs of various sizes and used them to extract information about the galaxies.
Using smaller-sized SOMs, we found that the data were clustered in 2 major groups; for each group, we found correlations that could not have otherwise been seen without clustering. 
In the maps with larger sizes, we created networks to illustrate the relative relations of the regions with one another. 
We then applied the SOMs that were generated from the M31 data to data from M101 and 
found that regions with similar properties in both galaxies were placed in close regions in the SOMs.  
These results confirm that the generated SOMs can separate regions based on their physical properties and can be used to make predictions for other regions in nearby galaxies or other targets. 
\end{abstract}
\begin{keywords} %PB: I think MNRAS only lets you have up to 6 and they are supposed to be from here: http://journals.aas.org/authors/keywords2013.html
galaxies: individual: M31, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing 
\end{keywords}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{../sections/}{intro0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{../sections/}{data0.0.tex}

@@

\import{../sections/}{method0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%\import{../sections/}{results0.0.tex}
\import{../sections/}{R10.0.tex}
\import{../sections/}{R20.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Discussion
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

%\import{../sections/}{caveat.tex}

@@

In self-organizing maps with larger sizes, networks can be used to illustrate the relations of the regions with one another.
We found the relative similarity between M31 regions by varying the size of the networks.
A one-dimensional network with 14 neurons was needed in order to
separate all 10 regions; some of the regions in M31 (e.g. regions 4 and 7) have very similar properties.
% PB joining paragraphs
Two-dimensional networks provide us with a more complete picture of the data.
We created various subsets of the input data and generated different networks which helped to show relations between regions in M31 more clearly.
Region 10 always becomes isolated in the networks, except when we  used only PAH data to create a network. %PB: remind the reader where regions 8 and 10 are
In that network region 10 blends more with other regions and only shows differences with the data from region 8.
These results suggest that the PAHs in all 10 regions have almost the same properties.

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
%\usepackage{mwe}    % loads »blindtext« and »graphicx«
\usepackage{slantsc}
\usepackage[latin1]{inputenc}   
\usepackage[T1]{fontenc}   
\usepackage[finnish]{babel}

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\mathrm {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\mathrm {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\mathrm {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\mathrm {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\mathrm {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\mathrm {star }}}
\newcommand \halpha    {H$\alpha $}
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \GALEX {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~\textsc{ii}]} 
\newcommand \oiii {[O~\textsc{iii}]} 
\newcommand \hi {H~\textsc{i}\ }
\newcommand \hii {H~\textsc{ii}\ }

@@

\begin{abstract} 
Galaxies are very complex systems; a complete understanding of them cannot be achieved only from studying linear or logarithmic correlations between their properties.
The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis. 
In the past few decades, a number of statistical methods have been developed and advanced to study and visualize complex datasets.
We used one of these methods to study the properties of nearby galaxies and create a clearer picture of them.
%Spatially resolved maps provide us with a unique view of the inside of galaxies. %and help better understand their properties.
In this project, we utilized the Kohonen Self Organizing Map (SOM) method to study observations of the nearby galaxies M31 and M101. %SOM is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data while preserving topological features of the original data. 
%We studied 10 regions in M31 and 8 regions in M101. 
%These regions were chosen based on the availability of mid-infrared spectroscopy data.
%For each region in M31, we had 46 data obtained through photometry, spectroscopy, and derived quantities (i.e., star formation rate, stellar mass, gas mass, etc.). 
%Using results from a correlation coefficient matrix, we reduced the dimension of this dataset and then trained the SOM using the new subset of data. 
We created SOMs of various sizes and used them to extract information about the galaxies.
Using smaller-sized SOMs, we found that the data were clustered in 2 major groups; for each group, we found correlations that could not have otherwise been seen without clustering. 
In the maps with larger sizes, we created networks to illustrate the relative relations of the regions with one another. 
We then applied the SOMs that were generated from the M31 data to data from M101 and
found that regions with similar properties in both galaxies were placed in close regions in the SOMs.  
These results confirm that the generated SOMs can separate regions based on their physical properties and can be used to make predictions for other regions in nearby galaxies or other targets. 
\end{abstract}
\begin{keywords} %PB: I think MNRAS only lets you have up to 6 and they are supposed to be from here: http://journals.aas.org/authors/keywords2013.html
galaxies: individual: M31, M101, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing 
\end{keywords}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{../sections/}{intro0.01.tex}

@@

\import{../sections/}{method0.01.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{../sections/}{data0.01.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%\import{../sections/}{results0.01.tex}
\import{../sections/}{R10.01.tex}
\import{../sections/}{R20.01.tex}

@@

In self-organizing maps with larger sizes, networks can be used to illustrate the relations of the regions with one another.
We found the relative similarity between M31 regions by varying the size of the networks.
A one-dimensional network with 14 neurons was needed in order to
separate all 10 regions; some of the regions in M31 (e.g. regions 4 and 7) have very similar properties.
Two-dimensional networks provide us with a more complete picture of the data.
We created various subsets of the input data and generated different networks which helped to show relations between regions in M31 more clearly.
Region 10 always becomes isolated in the networks, except when we  used only PAH data to create a network. %PB: remind the reader where regions 8 and 10 are
In that network region 10 blends more with other regions and only shows differences with the data from region 8.
These results suggest that the PAHs in all 10 regions have almost the same properties.

### 2016-07-13 sections/app_2d.tex
after Dave's comments

\newpage
\appendix
\section{2D SOMs of subsets}
        \import{../sections/image_texts/}{col3byall.tex}
        In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}. 
        IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
        Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
        The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
        In general by removing IRAC 5.7 $\mu$m  flux data from the input data, the colours between regions become much more darker.
        \import{../sections/tables/}{subset2.tex}
        \import{../sections/image_texts/}{subset2.tex}

        In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
        Since region 4 and 5 have a similar [~\oiii] and [~\sii] continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
        The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
        The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
        moreover, similar to regions 4 and 5, [~\oiii] and [~\sii] continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions. Therefore, they moved further from each other. 
        \import{../sections/tables/}{subset3.tex}
        \import{../sections/image_texts/}{subset3.tex}

@@

        The positions of the region 8 and 5 are moved closer in Fig.~\ref{fig: subset7}.
        Both of these regions are around the inner ring inside the galaxy.
        Therefore, both of them have similar values in most of the input parameters.
        However, they have very different fluxes in IRAC 5.7 $\mu$m and [~\sii] continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
        TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
        In Fig.~\ref{fig: subset7} the relations between all the other regions are mostly unchanged.
        \import{../sections/tables/}{subset7.tex}
        \import{../sections/image_texts/}{subset7.tex}

>>>>

\newpage
\appendix
\section{2D SOMs of subsets}
\label{sec: app_2d_soms_SOMN}

        We removed IRAC 5.7 $\mu$m; \sii continuum and \oiii continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, \oiii continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
        In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Tab.~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}. 
        IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
        Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
        For subset sample 7 (Tab.~\ref{tab: subset7}) we removed \sii flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 2 (~\ref{tab: subset5}).
        The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
        In general by removing IRAC 5.7 $\mu$m  flux data from the input data, the colours between regions become much more darker.
        \import{../sections/tables/}{subset2.tex}
        \import{../sections/image_texts/}{subset2.tex}

        In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
        Since region 4 and 5 have a similar \oiii and \sii continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
        The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
        The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
        moreover, similar to regions 4 and 5, \oiii and \sii continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions. Therefore, they moved further from each other. 
        \import{../sections/tables/}{subset3.tex}
        \import{../sections/image_texts/}{subset3.tex}

@@

        The positions of the region 8 and 5 are moved closer in Fig.~\ref{fig: subset7}.
        Both of these regions are around the inner ring inside the galaxy.
        Therefore, both of them have similar values in most of the input parameters.
        However, they have very different fluxes in IRAC 5.7 $\mu$m and \sii~continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
        TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
        In Fig.~\ref{fig: subset7} the relations between all the other regions are mostly unchanged.
        \import{../sections/tables/}{subset7.tex}
        \import{../sections/image_texts/}{subset7.tex}

### 2016-07-13 sections/intro0.01.tex
after Dave's comments

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction} 
% Nearby galaxies and their importance 
Nearby galaxies play an important role in our understanding of galaxies' formation and evolution.
These galaxies are close enough that we are able to observe regions inside them in detail.
As a result, many studies have been devoted to finding relations between physical properties of galaxies both in spatially-resolved regions and in galaxies as a whole%(Some more references here)
, and many others use these results in analyzing observations of high-redshift galaxies. %(Some more references here)
Advances in technology allow us to both observe and store enormous amounts of data from the sky.
Telescopes and surveys make observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc \citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from a distance.
M31 has been observed by many telescopes including the {\it Hubble}, \Spitzer, \Herschel space telescopes and has been the subject of many more studies.
\cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
Using data from the Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of M31's dust.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Massey07,Tamm12,Dalcanton12}
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.

Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of underlying processes in the galaxy.
The amount of observational data and measured quantities for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies.
However, to the best of our knowledge, this study is the first to use a data mining method on observations of nearby galaxies.

@@

%SOM
Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{ Hossein14,Hossein16}.
ANNs are designed to work in the same way that the neurons work in a human brain.
They are networks of interconnected neurons (nodes), in which all of the connections are weighted.
These networks are used to study nonlinear and complex relations between input and output data.
One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
SOMs map and visualize complex data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
Since the 1990s, many studies utilized SOMs for object classification and clustering (e.g. classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper %PB: MNRAS style guide says "Private communications or papers in preparation should be listed as such in the text, but omitted from the reference list, e.g. Smith (in preparation) shows that… " -- but I'm not clear on whether this applied to submitted papers or not

K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of clusters.
In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure. 
Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
We chose the SOM method over K-means due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
Therefore, we can cluster our sample data and study the underlying structure, simultaneously.

The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
There are very few studies on relations between properties of M31 with its PAH features.
To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
\cite{Cesarsky98} studied PAH spectra in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6\mu$m emission with enhanced 11.2~$\mu$m emission. 
However, \cite{Dim15} by using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
Using IRAC imaging observations,\cite{Barmby06} compared the observed 8~$\mu$m luminosity with other star formation indicators in the galaxy and found good agreement, and \cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.

%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
In this project we apply the self-organizing map algorithm to M31 data, training 1D and 2D networks.
Using the smaller networks we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM.
We apply the 2D trained networks to  observations of the Pinwheel Galaxy (M101), another nearby spiral  galaxy, to check whether it has similar properties.
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.

In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study. 
We describe the SOM method in Section $\S$~\ref{sec: method}. 
The results of the 1D SOM networks and the studying of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
In Section $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.

%SOM in Astronomy continued.
% Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
% These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
% finding patterns and common characteristics between galaxies can be a complex task.
% \citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
% They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
% They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
% Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
% The other application of SOMs is to find outliers or errors in the data.
% \citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline. This package can recognize an astronomical object from instrumental errors, and then classify the object based on its spectrum.

%Compare diff methods and say why we chose SOM!

%supervised and unsupervised network

>>>>

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction} 
% Nearby galaxies and their importance 
Nearby galaxies play an important role in our understanding of galaxies' formation and evolution.
Nearby galaxies are defined as those close enough that we are able to observe their structure and composition in detail.
As a result, many studies have been devoted to finding relations between physical properties of galaxies, such as morphology, star formation rate (SFR), stellar mass, metallicity, and amount of gas, both for spatially-resolved regions and galaxies as a whole~\citep[e.g.][]{Wong13,Leroy08}, and many others use these results in analyzing observations of high-redshift galaxies~\citep[e.g.][]{Freundlich13,Walch11}.
Advances in technology allow us to collect data from the sky.
Surveys such as KINGFISH~\citep{Kennicutt11} and THINGS~\citep{Walter08} have made observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Eskew12,Dale09,Calzetti07}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc, is the closest spiral galaxy to the Milky Way~\citep{McConnachie05}.
Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
M31 has been observed by many telescopes including the {\textit Hubble}, \Spitzer, \Herschel space telescope.
\cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
Using data from the Multiband Imaging Photometer for Spitzer (MIPS) instrument, \cite{Gordon06} studied the morphology of M31's dust.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied \hii~regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and~\cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.

Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of underlying processes in the galaxy.
What is the correlation between PAHs and SFR, dust mass, and gas mass in M31? 
Are PAHs features in M31 are similar or they can be divided in various groups? If so, what are properties of each group?
Does intensity of PAHs emission depends on the underlying structure of their position? 
How do they compare to properties of galaxies?
The properties of M31 that derived in various studies and observational data of this galaxy can be used for a knowledge discovery and data mining study.
%The amount of data for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
the Pinwheel Galaxy (M101), with distance of 6.7 Mpc~\citep{Freedman01}, is another nearby galaxies that has been observed and studied~\citep[e.g][and references therein]{Kennicutt11,Dale09, Leroy08, Gordon08}.
M101 is a large spiral galaxy with several \hii~regions and high metallicity gradient from centre to outskirt of it~\citep{Kennicutt03}.
In case of dimensionality data from M101 is a suitable addition to M31 data for a data mining study.
Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies.
However, this study is the first to use a data mining method on observations of nearby galaxies.

@@

The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
There are very few studies on relations between properties of M31 with its PAH features. %generate?!
\cite{Cesarsky98} studied PAH spectra in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6\mu$m emission with enhanced 11.2~$\mu$m emission. 
However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citealt[IRS,][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
Using IRAC imaging observations,~\cite{Barmby06} found good agreement between SFRs derived using observed 8~$\mu$m luminosity with other 
star formation indicators such as \halpha and far infrared luminosity in M31.
\cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
With data mining techniques we address that
compare to other galaxies, are PAHs features in M31 are unique as~\cite{Cesarsky98} mentioned or they are normal as ~\cite{Dim15} and \cite{Draine14} concluded

%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
In this project we apply the self-organizing map algorithm (SOM) to M31 data, training 1D and 2D networks.
Using the smaller networks we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM.
We apply the 2D trained networks to  observations of M101, another nearby spiral  galaxy, to check whether it has similar properties.
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.

We describe the SOM method in Section $\S$~\ref{sec: method}. 
In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
The results of the 1D SOM networks and the studying of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
In Section $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
